### 2017-06-15 paper.tex
adding other systems for lesson development, #8

The best way to choose tools for managing lessons
is to look for those that provide a gentle on-ramp for new contributors.
Ask potential contributors what they are comfortable with
rather than requiring \emph{them} to come to \emph{you}.
Remember also that contributing to a lesson is probably not their top priority,
and look for ways to reduce their cognitive load.
For example,
threaded discussion on particular topics (e.g., using GitHub issues)
can help increase the signal-to-noise ratio
by reducing long reply-all email excahnges.

>>>>

The best way to choose tools for managing lessons
is to look for those that provide a gentle on-ramp for new contributors.
Ask potential contributors what they are comfortable with
rather than requiring \emph{them} to come to \emph{you}.
Remember also that contributing to a lesson is probably not their top priority,
and look for ways to reduce their cognitive load.
For example,
threaded discussion on particular topics (e.g., using GitHub issues)
can help increase the signal-to-noise ratio
by reducing long reply-all email exchanges. 
A number of open frameworks are available to facilitate  
development of new lessons, such as R-based
learnr (\url{https://rstudio.github.io/learnr}) or 
GitHub-based Morea (\url{https://morea-framework.github.io}) and 
DataCamp (\url{https://www.datacamp.com/teach/documentation}).
